metric analysis

### 2021-07-09 metric_analysis.Rmd

```{r}
library(forcats)
f_imp_plot <- function(x) {
  ggplot(x, aes(fct_reorder(met_var, `%IncMSE`), `%IncMSE`)) + 
    geom_col() +
    coord_flip() +
    xlab("Met variable") +
    ggtitle(unique(x$variable))
}
lapply(split(filter(import, metric == "resistance"), ~ variable), f_imp_plot)

@@

```{r}
# Re-do above plots but now for resilience
lapply(split(filter(import, metric == "resilience"), ~ variable), f_imp_plot)
p_pdp <- p_pdp %+% filter(partial, metric == "resilience")
print(p_pdp + ylab("Resilience"))
```

@@

>>>>

```{r}
library(forcats)
f_imp_plot <- function(x) {
  ggplot(x, aes(fct_reorder(met_var, `%IncMSE`), `%IncMSE`)) + 
    geom_col() +
    coord_flip() +
    xlab("Met variable") +
    ggtitle(unique(x$variable))
}
xx <- lapply(split(filter(import, metric == "resistance"), ~ variable), f_imp_plot)

library(cowplot)
varimp_plot <- plot_grid(xx[["GPP"]], xx[["NEP"]], xx[["NPP"]], xx[["Rh"]])
print(varimp_plot)
save_plot("varimp_resistance.png", varimp_plot)

@@

```{r}
# Re-do above plots but now for resilience
xx <- lapply(split(filter(import, metric == "resilience"), ~ variable), f_imp_plot)
varimp_plot <- plot_grid(xx[["GPP"]], xx[["NEP"]], xx[["NPP"]], xx[["Rh"]])
print(varimp_plot)
save_plot("varimp_resilience.png", varimp_plot)

p_pdp <- p_pdp %+% filter(partial, metric == "resilience")
print(p_pdp + ylab("Resilience"))
```

@@

```{r}
# Combined partial dependence plot
partial %>% 
  mutate(metric = if_else(metric == "resistance", "Resistance", "Resilience")) %>% 
  ggplot(aes(x, y, color = variable)) + 
  geom_line() + 
  xlab("Meteorological variable value") + ylab("Metric value") +
  scale_color_discrete("") +
  facet_grid(metric ~ met_var, scales = "free") +
  theme(axis.text.x = element_text(angle = 90))
```
